Supporting Information : Complex and informative dependencies propogate throughout ecology and can be revealed using copulas

### 2019-05-14 SupportingInformation.Rmd
finally got the length down to journal limits again

\noindent The matrices from which root character states and changes 
across phylogeny branches were randomly chosen were generated as follows.
For extreme right-tail dependent noise, we first produced
a $1000000$ by $2$ matrix, $m$, of 
independent standard-normal random draws. Then, each row of $m$ 
was identified for a first set of modifications randomly 
and independently with a $50\%$ chance; 
for those rows identified, every element of the row was replaced with the 
absolute value of the first element of the row (including the first element itself).
For other rows, every element in the row was replaced by the negative of its
own absolute value. This produces right-tail dependent noise, normally distributed
for each location. If left-tail dependent noise was desired, we took the negative of the
entire matrix. The moderately left-tail dependent matrix was based on a C copula 
with parameter chosen (using the `iRho` function in the `copula` package) so that
the Spearman correlation would be the same as for the extreme tail dependence 
datasets. The moderately right-tail dependent matrix and the symmetric tail dependence
matrix were constructed similarly, but using an SC copula and an N copula,
respectively.

@@

Performing statistical tests for associations between continuous traits in different species
    was a primary motivating example of phylogenetic comparative methods.
For example, Felsenstein's method of phylogenetically independent contrasts 
    [@Felsenstein1985] is currently the second most-cited paper in the history
    of the journal the American Naturalist [@HueyGT2019].
Frustratingly, the field still lacks a dependable procedure for dealing with branch lengths, 
    which are a crucial input to the method.
Ideally, the branch lengths used to correct for phylogenetic effects would represent
    the expected amounts of change for the characters that are being analyzed.
Because researchers almost never have a reliable method for providing such branch lengths,
    most researchers rely on ultrametric trees -- those for which the branch
    length can be treated as a proxy for the duration of the branch in time.
Frequently these branch lengths are transformed to assess sensitivity to different 
    assumptions about the degree of phylogenetic inertia displayed by the traits
    under study [@Ives2018;@Harmon2018].
Even if one were able to simply use a time-based set of branch lengths, assigning
    dates to nodes in phylogenies is difficult.
DNA sequence data can provide estimates of branch lengths, but these estimates
    are dependent on the adequacy of models which correct sequences for multiple
    substitutions occurring at the same location.
Biases in estimating the evolutionary distance can affect down stream analyses [@Phillips2009].
Additionally, changes
    in the rate of molecular evolution make the estimation of dates difficult [@HeathM2014] even when branch lengths in time are accurately estimated.

@@

Additionally, character evolution was simulated using one random draw from the relevant matrix
per phylogeny branch. This was principally because branch lengths are often hugely
uncertain. If branch lengths were well know, alternative simulation strategies may
include selecting one draw from the matrix of evolutionary changes per unit time, 
or selecting one draw for the whole branch but rescaling variance according to the 
length of the branch. These choices amount to the same thing for normal copula
structure, but not otherwise. Modelling choices such as these may have influenced
our results. Additional research also seems warranted testing the realism 
of our hypothesized mechanism and simulations.

>>>>

\noindent The matrices from which root character states and changes 
across phylogeny branches were randomly chosen were generated as follows.
For extreme right-tail dependent noise, we first produced
a 1,000,000 by $2$ matrix, $m$, of 
independent standard-normal random draws. Then, each row of $m$ 
was identified for a first set of modifications randomly 
and independently with a $50\%$ chance; 
for those rows identified, every element of the row was replaced with the 
absolute value of the first element of the row (including the first element itself).
For other rows, every element in the row was replaced by the negative of its
own absolute value. This produces right-tail dependent noise, normally distributed
for each location. If left-tail dependent noise was desired, we took the negative of the
entire matrix. The moderately left-tail dependent matrix was based on a C copula 
with parameter chosen (using the `iRho` function in the `copula` package) so that
the Spearman correlation would be the same as for the extreme tail dependence 
datasets. The moderately right-tail dependent matrix and the symmetric tail dependence
matrix were constructed similarly, but using an SC copula and an N copula,
respectively.

@@

Performing statistical tests for associations between continuous traits in different species
    was a primary motivating example of phylogenetic comparative methods.
For example, Felsenstein's method of phylogenetically independent contrasts 
    [@Felsenstein1985] is currently the second most-cited paper in the history
    of the journal the American Naturalist [@HueyGT2019].
Frustratingly, the field still lacks a dependable procedure for dealing with branch lengths, 
    which are a crucial input to the method.
Ideally, the branch lengths used to correct for phylogenetic effects would represent
    the expected amounts of change for the characters that are being analyzed.
Because researchers almost never have a reliable method for providing such branch lengths,
    most researchers rely on ultrametric trees -- those for which the branch
    length can be treated as a proxy for the duration of the branch in time.
Frequently these branch lengths are transformed to assess sensitivity to different 
    assumptions about the degree of phylogenetic inertia displayed by the traits
    under study [@Ives2018;@Harmon2018].
Even if one were able to simply use a time-based set of branch lengths, assigning
    dates to nodes in phylogenies is difficult.
DNA sequence data can provide estimates of branch lengths, but these estimates
    are dependent on the adequacy of models which correct sequences for multiple
    substitutions occurring at the same location.
Biases in estimating the evolutionary distance can affect downstream analyses [@Phillips2009].
Additionally, changes
    in the rate of molecular evolution make the estimation of dates difficult [@HeathM2014] even when branch lengths in time are accurately estimated.

@@

Additionally, character evolution was simulated using one random draw from the relevant matrix
per phylogeny branch. This was principally because branch lengths are often hugely
uncertain. If branch lengths were well known, alternative simulation strategies may
include selecting one draw from the matrix of evolutionary changes per unit time, 
or selecting one draw for the whole branch but rescaling the variances of the selected
character changes according to the 
length of the branch. These choices amount to the same thing for normal copula
structure, but not otherwise. Modelling choices such as these may have influenced
our results. Additional research also seems warranted testing the realism 
of our hypothesized mechanism and simulations.
